---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```



## Topic 1: Using R

### Use R as a calculator 

Write ```2 + 2``` in the following code chunk:

```{r two-plus-two, exercise=TRUE}

```

Write the R code required to multiply six times seven:

```{r six-times-seven, exercise=TRUE}

```

So we can use R as a calculator. Cool.

Now write ```"Arr!"```. Don't forget the quotes:
```{r arr, exercise=TRUE}

```

That was not a number. That was not *numeric*. That was a *character*, a *string*.

Everything between quotes is considered a string. Try to write ```"2+2+"```; this is also a string! 
```{r string-sum, exercise=TRUE}

```

Double quotes, single quotes, all are the same (just do not mix them). Write now ```'Arr! in single quotes'```. 
```{r arr-single, exercise=TRUE}

```

Let's move now to *boolean* values. Write ```TRUE```, ALL IN CAPS, no quotes.
```{r true, exercise=TRUE}

```

Write now ```FALSE```, ALL IN CAPS, no quotes.
```{r arr-single, exercise=TRUE}

```

Note that the programming language R did not add quotes to those words. ```TRUE``` and ```FALSE``` are *reserved* words.

## Topic 2: Vectors

## Topic 3: Matrices

## Topic 4: Summary Statistics

## Topic 5: Factors

## Topic 6: Data Frames



## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-twoo, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

